%! Author = ruochongli
%! Date = 2023/3/11

% Preamble
\documentclass[./main.tex]{subfiles}

% Packages

% Document
\begin{document}

    \begin{thebibliography}{99}
        \bibitem.Hu Ge, Peng Shuai, Zhang Sheng-tao.\emph{Research on Numerical Simulation for Transmission of Contaminants in Soil}[J].Chinese Journal of Environmental Engineering.vol.4, no.7(2010)
        \bibitem.Zhu Jian-jun.\emph{Research on Some Problems of the Analytic Hierarchy Process and Its Application}[D].Shenyang:Northeastern University,2005.
        \bibitem.Qiu Bing-wen, Chen Chong-cheng.\emph{Land Use Change Simulation Model Based on MCDM and CA and Its Application}[J].Acta Geographica Sinica.vol.63, no.2(2008),165-174.
        \bibitem.Li Mei-juan, Chen Guo-hong.\emph{A Review on the Research and Application of DEA}[J].Engineering Science.vol.5, no.6(2003),88-94.
        \bibitem.Bai Wan-qi, Zhao Shi-dong.\emph{A Comprehensive Description of the Models of Land Use and Land Cover Change Study}[J].Journal of Natural Resources.vol.12, no.2(1997),169-175.
        \bibitem.Chen Zhi-zong, You Jian-xin.\emph{A Multi-objective Decision Model of Emergency Rescue Facility Location for Large Scale Emergency Incidents}[J].Managements Science in China.vol.19,no.4(2006),10-14.
        \bibitem.Wang Qi-fan.\emph{New Progress in Theory and Methodology of System Dynamics}[J].System Engineering -Theory Methodology Applications.vol.4, no.2(1995),6-12.
        \bibitem.Ga0 Feng, Sun Cheng-quan, Liu Quan-gen.\emph{The Status and Trends of Solar Energy Utilization}[J].Science and technology frontier and academic review.vol.23, no.4(2001),35-39.
        \bibitem.Yeneayehu Fenetahun, Xu Xin-wen, You Yuan, Wand Yong-dong.\emph{Effects of Vegetation Cover, Grazing and Season on Herbage Species Composition and Biomass: A Case Study of Yabello Rangeland, Southern Ethiopia}[J].Journal of Resources and Ecology.vol.11, no.2(2020),159-170.
        \bibitem.Zhang Cheng-cai, Chen Ji-zu, Li Hong-wei.\emph{Industrial Point Sources of Air Pollution Dispersion Simulation Based on GIS and Surfer}[J].Safety and Environmental Engineering.vol.16, no.5(2009),48-52.
        \bibitem.Fu Xiao-liang.\emph{Research on the Contaminant Transport in Soil}[J].Hangzhou:Zhejiang University,2004.
        \bibitem.Li Jing-yin, Gao Tai-zhong, Guo Yu-feng.\emph{Experimental Study on Transport and Transformation of
        Organic Pollutants in Cihe Wastewater in Saturated Soil}[J].Research of Environmental Sciences.vol.15, no.3(2002),49-52.
        \bibitem.Wang Qing-gai, Zhao Xiao-hong, Wu Wen-jun, Yang Mu-shui, \textit{et al}.\emph{Advection-diffusion models establishment of water-pollution accident in middle and lower reaches of Han-jiang river}[J].Advances in Water Science.vol.19, no.4(2008),500-504.
        \bibitem.Lan Yong, Liu Shun-jia, Xiang Ping-an.\emph{Quantifying the   Pollution Loading from Livestock and
        Poultry of Family Farm —Based on the Sample of Counties in Hunan Province}[J].Economic Geography.vol.35, no.10(2015),187-193.
        \bibitem.Ma Hong-wei, Li Xiao, Cui Jian, Yang Ze.\emph{A Preliminary Study on the Organic and Inorganic Pollution of Groundwater of Jiansanjiang Farm in Sanjiang Plain}[J].Geology and Resources.vol.23, no.1(2014),169-175.
        \bibitem.Li Hua-lin, Zhang Shou-hong, Yu Pei-dan \textit{et al}.\emph{Estimation and Critical Source Areas
        Identification of Non-Point Source Pollution Based on Improved Export Coefficient Models: A Case Study of the Upper Beiyun River Basin}[J].Environmental Science.(2023).10.13227/j.hjkx.202211321.
        \bibitem.Tony Prato, Shi Hong-qi, \textit{et al}.\emph{Soil Erosion and Non-point Source Pollution Control in Idaho Small Watershed}[J].Environmental Science.(2023),169-175.[J].Soil and Water Consevation.no.4(1989).
        \bibitem.Li Hong-wei, Liu Jia-jia, Li Cheng-lin.\emph{Research on the Simulation of Water Pollution in River Based on GIS}[J].Environmental Science and Management.vol.32,no.2(2007),126-128.
        \bibitem.Li Hong-wei, Liu Jia-jia, Li Cheng-lin.\emph{Research on the Simulation of Water Pollution in River Based on GIS}[J].Environmental Science and Management.vol.32,no.2(2007),126-128.
        \bibitem.Su Zhi-hui, Wu Bing, Gong Yuan-shi.\emph{Determination of gas diffusion coefficient in soils with different porosities}[J].Transactions of the Chinese Society of Agricultural Engineering.vol.31,no.15(2015),108-113.
        \bibitem.Zhang Wen-jie, Zhao Pei, Jia Wen-qiang.\emph{Boundary conditions of one-dimensional convection -diffusion column tests and unified analytical solution}[J].Rock and Soil Mechanics.vol.36,no.10(2015),28-33.
    \end{thebibliography}

\end{document}