%! Author = ruochongli
%! Date = 2023/3/9

% Preamble
\documentclass[./main.tex]{subfiles}

% Packages

% Document
\begin{document}
    \section{Introduction}
    \subsection{Background}
    A decision-maker faced the task of deciding on the best use for a 3-square-kilometer parcel of land
    located in Syracuse, NY, USA .
    The property experiences a marine climate with all four seasons, including snowy winters, and has adequate water and power supplies.
    It is located 50 kilometers away from urban areas of the city, with adequate road and transit systems.
    In October 2022, the concept of building a semiconductor fabrication facility in Clay, NY, just north of Syracuse, was proposed to increase the employment rate.


    \subsection{Restatement of the Problem}
    The problem at hand is to determine the optimal use of a 3-square-kilometer area in Syracuse, taking into account various factors such as geography, climate, business opportunities, community needs, and local culture.

    To achieve this, we must first establish a series of metrics in order to give a  clear definition of \lq\lq{best use}\rq\rq, which can instill
    confidence in
    the decision maker regarding the final use of the land.

    Next, we must select at least two options from the list of facilities and evaluate them according to the
    established metrics of \lq\lq{best use}\rq\rq.
    We should identify the key factors of the metrics and support
    their
    reasoning with specific data.
    This will allow us to defend their metrics against challenges and ensure that their results are consistent with reality.
    The introduction of the Micron Technology semiconductor fabrication facility, which is expected to employ up to $9,000$ people with an additional $40,000$
    jobs among suppliers, construction firms, and other businesses, is an external factor that must be considered.
    We should re-evaluate the options after this change and test the sensitivity of our metrics.

    Finally, the team should assess the suitability of the model by using it to evaluate a familiar environment and
    determine how generalizable the model is.
\end{document}